Visual proteomics using whole-lamella 2D template matching

### 2022-01-05 manuscript.tex
new name [ci skip]
This build is based on
https://github.com/jojoelfe/fowl_template_matching_manuscript/commit/4eeafd31bd521c439395837768989d548d581f72.

This commit was created by the following CI build and job:
https://github.com/jojoelfe/fowl_template_matching_manuscript/commit/4eeafd31bd521c439395837768989d548d581f72/checks
https://github.com/jojoelfe/fowl_template_matching_manuscript/actions/runs/1658913730

This manuscript
(\href{https://jojoelfe.github.io/fowl_template_matching_manuscript/v/3fd92a26614a26949905aec5a87c6e0dabaffd3a/}{permalink})
was automatically generated
from \href{https://github.com/jojoelfe/fowl_template_matching_manuscript/tree/3fd92a26614a26949905aec5a87c6e0dabaffd3a}{jojoelfe/fowl\_template\_matching\_manuscript@3fd92a2}
on January 4, 2022.

>>>>

This manuscript
(\href{https://jojoelfe.github.io/fowl_template_matching_manuscript/v/4eeafd31bd521c439395837768989d548d581f72/}{permalink})
was automatically generated
from \href{https://github.com/jojoelfe/fowl_template_matching_manuscript/tree/4eeafd31bd521c439395837768989d548d581f72}{jojoelfe/fowl\_template\_matching\_manuscript@4eeafd3}
on January 5, 2022.
